---
title: "R卡片1：R基础和控制结构简介"
author: "yb"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 注释
  # 从#号开始到这一行结束均为注释，r不会执行这一行代码
  
## 基本数据类型

1) `logical`  #逻辑型，包含布尔值TRUE和FALSE

2) `integer` #32位整数

3) `double` #双精度实数

4) `character` #字符型

5) `complex` #复数型 (3+2i)

注意: 整型和双精度型均为数值型（`numeric`）

# R数据结构

1) `atomic vector` #原子向量，长度为1-N，所有的元素只能是同一种数据类型，元素可以命名。R没有标量的概念，单个的数字或者字符实际上是长度为1的向量。

2) `list` #列表，长度为1-N，可以是任何R对象，甚至包括列表自身，列表的元素可以是不同类型的对象，元素可以命名。

3) `factor` #因子，长度为1-N，有序或分类的数据，通常是字符型，但底层存储为整型。

4) `data.frame` #1-M行，1-N列,每一列通常是一个变量，表现为向量类型或者因子类型，行可命名。

5) `matrix` #2维数值向量，1-M行，1-N列，行和列都可命名。

6) `array` – essentially a matrix with

(typically) 3 or more dimensions

Note: While these are the most common

objects used for analysis, most things in R

are objects that can be manipulated.

Note: Some objects only contain certain

types (eg. matrix), or everything in the

object is of the same type (eg. vector)

# 对象索引

Because objects contain multiple values,

understanding indexing is critical to R:

1) `x[i], x[r, c]` – can select multiple

2) `x[[i]], x[[r, c]]` – select single

3) `x$i, x$"i"` – select single by name

a) by number: `x[5]; x[1:10]; x[length(x)]`

b) by logic: `x[T,F,T,F]; x[!is.na(x)]`

c) by name: `x['me']; x$me; x[c('a', 'b')]`

Note: 2-dimension indexes are x[row, col]

Trap: x[i] and x[[i]] can return very

different results from the same object

# 类

R has class mechanisms for creating more

complex data objects. Common classes

include Date, ts (time series data), lm

(the results of a regression linear model).

These are often used like other objects.

# 对象和变量

Objects can be assigned to variables: <-

Note: objects have mode/type, not variables

Note: if an object has a rule your code

will be quietly coerced to meet the rule:

`x <- c(1, "2"); cat(x)` # -> "1", "2"

# 查看对象的属性

1) `typeof(x)` – the R type of x

2) `mode(x)` – the data mode of x

3) `storage.mode(x)` – the storage mode of x

4) `class(x)` – the class of x

5) `attributes(x)` – the attributes of x

(common attributes: 'class' and 'dim')

6) `str(x)` – print a summary structure of x

7) `dput(x)` – print full text R code for x

# 缺失值和不存在的值

1) `NULL` is an object, typically used to

mean the variable contains no object.

2) `NA` is a value that means: missing data

item here


```{r}
x <- NULL; is.null(x); y <- NA; is.na(y);length(NULL); length(NA)
```


# -> 0, 1

Trap: can have a list of NULLs but not a

vector of NULLs. Can have a vector of NAs.

# 其他非数字的数值对象

1) `Inf` # positive infinity

2) `-Inf` # negative infinity

3) `NaN` # not a number

1/0; 0/0 # -> Inf, NaN

# 操作符

`+, -, *, /` # addition, subtraction,

 # multiplication, division

`^ or **` # exponentiation

`%%` # modulus

`%/%` # integer division

`%in%` # membership

`:` # sequence generation

`<, <=, ==, >=, >, !=` # Boolean comparative

`|, ||` # (vectorised/not vec)

`&, &&` # (vectorised/not vec)

Note: with few exceptions (&&, || and :)

operators take vectors and return vectors.

# 流程控制结构

1) `if (cond) expr`

2) `if (cond) expr1 else expr2`

3) `for (var in seq) expr`

4) `while (cond) expr`

5) `repeat expr`

Note: break exits a loop, next moves flow

to the start of the loop with the next var

Note: expressions typically enclosed in {}

But single expressions do not need the {}

Multiple expression on a line ; separated

# 流程控制函数

1) the vectorised if statement:

`result <- ifelse(cond, expr1, expr2)`

2) the switch statement (not vectorised):


```{r eval = FALSE}
switch( expr.string,

case1 = expr1,

case2 = expr2,

default = expr 3 # default optional)

```

expr.string evaluates to a char string

Note: cases not enclosed in quotes.


